The Right Way to Search Evolving Graphs

### 2016-02-26 paper.tex
fix typo

The complexity of the algebraic BFS of Algorithm \ref{alg:bfsla} is significantly
more complicated that that of Algorithm \ref{alg:bfs}. While the latter uses the
usual adjacency list representation for graphs, the computational cost of the
former depends critically on the actual representation of the matrices.
Furthermore, the average case analysis is complicated by the expected fill-in of
the vector $\bm b$, which influences the cost of the matrix-vector product on line 7
and the expected number of iterations of the \textbf{while} loop beginning on line6.

>>>>

The complexity of the algebraic BFS of Algorithm \ref{alg:bfsla} is significantly
more complicated that that of Algorithm \ref{alg:bfs}. While the latter uses the
usual adjacency list representation for graphs, the computational cost of the
former depends critically on the actual representation of the matrices.
Furthermore, the average case analysis is complicated by the expected fill-in of
the vector $\bm b$, which influences the cost of the matrix-vector product on line 7
and the expected number of iterations of the \textbf{while} loop beginning on line 6.
